Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-17 paper/paper.Rmd
violing plot tweaks

Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a violin plot. Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.

@@

# violin plot
t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self)) +
  geom_violin(scale = "width") + ylim(0,0.08) +
  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
  facet_wrap(~ type) +
  xlab("Amount of faces found") +
  ylab("Time taken per image (Seconds)")

>>>>

Figure \@ref(fig:timeFigure) displays the distribution of processing time required by the APIs for each image, as a violin plot (REF). Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.

@@

# violin plot
t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self, fill=type)) +
  geom_violin(scale = "count", alpha=0.5, adjust=0.01) + ylim(0,0.08) +
  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
  facet_wrap(~ type) +
  xlab("Amount of faces found") +
  ylab("Time taken per image (Seconds)") + scale_fill_manual("", values=type.colours) +
  geom_smooth(aes(x=n, time.sys.self), method="lm", se=F, colour="black") + 
  scale_colour_manual("", values=type.colours)
